Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-22 tex/background.tex
more precision in 2(c)

\item[$\triangleright$] Verification must precede validation.
\item[$\triangleright$] The need for validation experiments and the associated accuracy requirements for computational model predictions are based on the intended use of the model.
\item[$\triangleright$] Validation of a complex system should be pursued in a hierarchical fashion from the component level to the system level.
\item[$\triangleright$] Validation is specific to a particular computational model for a particular intended use.
\item[$\triangleright$] Validation must assess the predictive capability of the model in the physical realm of interest, and it
must address uncertainties that arise from both simulation results and experimental data.

@@

When studying both surface phonon polaritons and surface plasmon resonances, one can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.

>>>>

\item[$\triangleright$] Verification must precede validation.
\item[$\triangleright$] Needs for validation experiments and associated accuracy requirements for computational model predictions are based on the intended use of the model.
\item[$\triangleright$] Validation of a complex system should be pursued in a hierarchical fashion from the component level to the system level.
\item[$\triangleright$] Validation is specific to a particular computational model for a particular intended use.
\item[$\triangleright$] Validation must assess the predictive capability of the model in the physical realm of interest, and it
must address uncertainties that arise from both simulation results and experimental data.

@@

When studying both surface phonon polaritons and surface plasmon resonances, one can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, absorption, or extinction cross-section (scattering plus absorption), as well as reflection. 
Since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen, 
these different approaches are comparable in some cases, e.g., whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.
